Exponential Integrals\\ [1ex]

### 2022-02-23 draft2.tex

and Mathematica gives the following solutions
\begin{align*}
\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &  
\end{align*}
Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
\begin{align*}
\hat{u}_+(\zeta)&=C_1 T_{-2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-2/3}\hat{w}_+(\zeta)\\
\hat{u}_-(\zeta)&= C_2 T_{2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{2/3}\hat{w}_-(\zeta) & \\
\end{align*}

@@

These are evidence of the resurgent properties of $\tilde{I}_{\pm 1}(z)$.

\begin{lemma}
The following identity holds true
\begin{equation}
{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}\qquad \qquad \zeta=u+\frac{1}{u}
\end{equation}
\end{lemma}
\begin{proof}
From 15.4.13 DLMF, we have
\begin{align*}
{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)&=\frac{2}{\sqrt{4-\zeta^2}} & y=\mathrm{arccsc}(\zeta/2)\\
&=\frac{1}{\sqrt{1-\mathrm{csc}^2(y)}} & \\
&=-i\tan(y) &   \zeta=\frac{2}{\sin(y)}
\end{align*}
therefore if $u=\tan\left(\frac{y}{2}\right)$, we have $\zeta=\frac{1+u^2}{u}=f(u)$ and 
\begin{equation*}
{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}=\frac{2i}{f'(u)u}
\end{equation*}  
\end{proof}

\begin{claim}
\label{Bessel}
\begin{equation}
\hat{w}_{+}(\zeta-2)=i\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'\,\qquad \zeta\in(2,+\infty)
\end{equation}
\end{claim}
\begin{proof}
Let us first consider the RHS of \eqref{Bessel}
\begin{align*}
&2\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'= &\\
&\quad = \frac{4}{3}\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]d\zeta' &\\
&\quad =\frac{8}{3}\int_0^x(y-x)^{-1/2}\left[{}_2F_1\left(2,2,;\frac{5}{2};y\right)-{}_2F_1\left(2,2;\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0)\\
&\quad =2\pi\int_0^x(x-y)^{-1/2}y^{-2}F\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \eqref{4.8} \\
&\quad =\pi^2|x|^{-3/2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) & x\in (-\infty, 0)\\
&\quad =\frac{\pi^2}{2}\left({}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}-\frac{\zeta}{4}\right)-i{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)\right) & \zeta\in(2,+\infty)
\end{align*}
however ${}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2,+\infty)$, thus the claim holds true. 
\end{proof}
Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
\end{example}

@@

\begin{multline}
\label{w1w3w5}
{}_2F_1\left(a,b;c;z\right)=e^{b\pi i}\frac{\Gamma(c)\Gamma(a-c+1)}{\Gamma(a+b-c+1)\Gamma(c-b)}{}_2F_1\left(a,b;c;1-z\right)+\\
-e^{(a+b-c)\pi i}\frac{\Gamma(c)\Gamma(a-c+1)}{\Gamma(b)\Gamma(a-b+1)}|z|^{-a}{}_2F_1\left(a,a-c+1;a-b+1;\frac{1}{z}\right)
\end{multline}

\begin{multline}
\label{4.5}
\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)(x-y)^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
\end{multline}
which can be rewritten as \textbf{(\texttt{arXiv:1504.08144}, formula~4.8)}
\begin{multline}
\label{4.8}
\int_{y>x}|y|^{-a}|x-y|^{\mu-1}{}_2F_1\left(a,b;c;y^{-1}\right)dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{-a+\mu}{}_2F_1\left(a-\mu,b;c;x^{-1}\right)\\
x\in(-\infty,0)\cup(1,\infty), \, \Re a>\Re\mu>0
\end{multline}
%\textcolor{red}{We should check that for Hypergeomtric functions the following relation holds true
%\[{}_2F_1(a,b;c;z-1)\propto\int_1^z(z-t)^{-1/2}\left[{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};1-t\right)-{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};t\right)\right]dt\]
%}
%
%The following identities hold true
%\begin{multline}
%\label{a+b+c+}
%\int_{0<\frac{y}{x}<1}|y|^{c-1}(1-y)^{a+b-c}{}_2F_1\left(a,b;c;y\right)\frac{|x-y|^{\mu-1}}{\Gamma(\mu)}dy=\\
%\frac{\Gamma(c)}{\Gamma(c+\mu)}|x|^{c-1+\mu}(1-x)^{a+b-c+\mu}{}_2F_1\left(a+\mu,b+\mu;c+\mu;x\right)\\
% x\in (-\infty,0)\cup(0,1), \,\Re c>0,\,\Re\mu>0
%\end{multline}
%
%\begin{multline}\label{a-b-c-}
%\int_{-\infty}^x{}_2F_1\left(a,b;c;y\right) (x-y)^{\mu-1}dy=\Gamma(\mu)\frac{\Gamma(a-\mu)}{\Gamma(a)}\frac{\Gamma(b-\mu)}{\Gamma(b)}\frac{\Gamma(c)}{\Gamma(c-\mu)}{}_2F_1\left(a-\mu,b-\mu;c-\mu;x\right)\\
%x<1, \Re a,\Re b>\Re\mu>0
%\end{multline}

>>>>

and Mathematica gives the following solutions
\begin{align*}
\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &  
\end{align*}
Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
\begin{align*}
\hat{u}_+(\zeta)&=C_1 T_{-\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-\tfrac{2}{3}}\;\hat{w}_+(\zeta)\\
\hat{u}_-(\zeta)&= C_2 T_{\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{\tfrac{2}{3}}\;\hat{w}_-(\zeta)
\end{align*}

@@

These are evidence of the resurgent properties of $\tilde{I}_{\pm 1}(z)$. \textbf{Hopefully, the latter identities show that the Stokes constants can be computed via Alien calculus and they are equal to $\pm 2$.  }

Now we show that the fractional derivative formula holds in this example: first we write a parametrization of the integration path in the Borel plane. Let $\mathcal{C}_p=\R$, $p\in \pi\Z$, be the contour of integration in $\tilde{\C}$ which is parametrized as

\begin{align*}
{C}_p\colon \R & \to \tilde{\C} \\
\theta & \to \theta+i p
\end{align*}

Then in the Borel plane $\C_\zeta$, where $\zeta=2\cosh(u)$, the path $\mathcal{C}_0$ is parametrized as  
\begin{align*}
\mathcal{C}_0\colon\R &\to \C_\zeta \\
\theta & \to 2\cosh(\theta)
\end{align*}

\begin{figure}
\caption{Integration path in the $u$-plane and in the Borel plane $\zeta=2\cosh(u)$. }
\end{figure}

\textbf{Check Aaron notation}

\begin{equation}
\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)=\int_{\mathcal{C}_0(\zeta)}du=\Big[ u\Big]^{\mathrm{end}\mathcal{C}_0(\zeta)}_{\mathrm{start}\mathcal{C}_0(\zeta)}=2\mathrm{arc}\cosh\left(\frac{\zeta}{2}\right)
\end{equation}

We can now write $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ as an hypergeometric function thanks to identity 14.4.4 \cite{DLMF}: set $\xi=\frac{1}{2}\left(\frac{1}{2}\zeta-1\right)=\frac{1}{2}\left(\cosh(\theta)-1\right)=\sinh^2\left(\frac{\theta}{2}\right)$, then

\begin{align*}
\sinh\left(\frac{\theta}{2}\right)\,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};\sinh^2\left(\frac{\theta}{2}\right)\right)&=i\frac{\theta}{2} \\
\xi^{1/2}{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi\right)&=i\frac{\theta}{2}\\
 &=\frac{i}{2}\left(\frac{1}{2}\mathrm{arcosh}\left(\frac{\zeta}{2}\right)\right)\\
 &=\frac{i}{4}\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)
\end{align*}

The $3/2$-derivative of $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ can be computed as follows: we compute the $-1/2$-derivatve and then we differentiate twice

\begin{align*}
\partial_{\zeta}^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_2^\zeta (\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)d\zeta'\\
&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^{\xi}\frac{1}{2}(\xi-\xi')^{-1/2}(-4i)\xi'^{1/2} {}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi'\right) 4d\xi'\\
&=-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)
\end{align*}

\begin{align*}
\partial_\zeta^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \\
&=\frac{1}{16}\partial_\xi^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \partial_\xi=4\partial_\zeta\\
&=+\frac{i}{2}\Gamma\left(\frac{3}{2}\right)\partial_\xi\left({}_2F_1\left(\frac{1}{2},\frac{1}{2};1,-\xi\right)\right) & \textbf{DLMF} 15.5.4\\
&=-\frac{i}{8}\Gamma\left(\frac{3}{2}\right){}_2F_1\left(\frac{3}{2},\frac{3}{2};2,-\xi\right) & \\
&=-\frac{i\sqrt{\pi}}{16}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2,\frac{1}{2}-\frac{\zeta}{4}\right) & \\
&=-\frac{i\sqrt{\pi}}{16} \hat{w}_+(\zeta-2) &
\end{align*}

%Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
\end{example}

@@

\begin{multline}
\label{w1w3w5}
{}_2F_1\left(a,b;c;z\right)=e^{b\pi i}\frac{\Gamma(c)\Gamma(a-c+1)}{\Gamma(a+b-c+1)\Gamma(c-b)}{}_2F_1\left(a,b;c;1-z\right)+\\
-e^{(a+b-c)\pi i}\frac{\Gamma(c)\Gamma(a-c+1)}{\Gamma(b)\Gamma(a-b+1)}|z|^{-a}{}_2F_1\left(a,a-c+1;a-b+1;\frac{1}{z}\right)
\end{multline}
%\begin{multline}
%\label{4.1}
%\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)|x-y|^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
%x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
%\end{multline}

\begin{multline}
\label{4.5}
\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)|x-y|^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
\end{multline}
which can be rewritten as \textbf{(\texttt{arXiv:1504.08144}, formula~4.8)}
\begin{multline}
\label{4.8}
\int_{y>x}|y|^{-a}|x-y|^{\mu-1}{}_2F_1\left(a,b;c;y^{-1}\right)dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{-a+\mu}{}_2F_1\left(a-\mu,b;c;x^{-1}\right)\\
x\in(-\infty,0)\cup(1,\infty), \, \Re a>\Re\mu>0
\end{multline}
%\textcolor{red}{We should check that for Hypergeomtric functions the following relation holds true
%\[{}_2F_1(a,b;c;z-1)\propto\int_1^z(z-t)^{-1/2}\left[{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};1-t\right)-{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};t\right)\right]dt\]
%}
%
%The following identities hold true
%\begin{multline}
%\label{a+b+c+}
%\int_{0<\frac{y}{x}<1}|y|^{c-1}(1-y)^{a+b-c}{}_2F_1\left(a,b;c;y\right)\frac{|x-y|^{\mu-1}}{\Gamma(\mu)}dy=\\
%\frac{\Gamma(c)}{\Gamma(c+\mu)}|x|^{c-1+\mu}(1-x)^{a+b-c+\mu}{}_2F_1\left(a+\mu,b+\mu;c+\mu;x\right)\\
% x\in (-\infty,0)\cup(0,1), \,\Re c>0,\,\Re\mu>0
%\end{multline}
%
%\begin{multline}\label{a-b-c-}
%\int_{-\infty}^x{}_2F_1\left(a,b;c;y\right) (x-y)^{\mu-1}dy=\Gamma(\mu)\frac{\Gamma(a-\mu)}{\Gamma(a)}\frac{\Gamma(b-\mu)}{\Gamma(b)}\frac{\Gamma(c)}{\Gamma(c-\mu)}{}_2F_1\left(a-\mu,b-\mu;c-\mu;x\right)\\
%x<1, \Re a,\Re b>\Re\mu>0
%\end{multline}
